R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-23 manuscript.Rmd

      Discussion. Programmatic acccess to GBIF will facilitate more open
        and reproducible science - the three GBIF clients described herein
        are a significant contribution towards this goal.

@@

In Python, we can similary search for datasets. Here, search for datasets of type
`OCCURRENCE`:

@@

The download service, like the occurrence search service, is rate-limited.
That is, you can only have one to three downloads running simultaneously for
your user credentials. However, simply check when a download job is complete,
then you can start a new download request. See "Queueing Download Requests"
below for help automating many download requests in R.

@@

The Ruby library `gbifrb` does not yet have occurrene download functionality.

@@

Both R and Python are commonly used in science, and can be used for similar
tasks. Python, however, is a more general programming lanugae, and can be
used in more contexts than R can be used in. Ruby is used very little in
science; but, like Python, Ruby is very widely used as a general purpose
programming language, with heavy use in web development and web services.

>>>>

      Discussion. Programmatic access to GBIF will facilitate more open
        and reproducible science - the three GBIF clients described herein
        are a significant contribution towards this goal.

@@

In Python, we can similarly search for datasets. Here, search for datasets of type
`OCCURRENCE`:

@@

The download service, like the occurrence search service, is rate-limited.
That is, you can only have one to three downloads running simultaneously for
your user credentials. However, simply check when a download job is complete,
then you can start a new download request. See "Queuing Download Requests"
below for help automating many download requests in R.

@@

The Ruby library `gbifrb` does not yet have occurrence download functionality.

@@

Both R and Python are commonly used in science, and can be used for similar
tasks. Python, however, is a more general programming language, and can be
used in more contexts than R can be used in. Ruby is used very little in
science; but, like Python, Ruby is very widely used as a general purpose
programming language, with heavy use in web development and web services.
